{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-08-06 documents/paper.tex
Slide 1 done!
gosh writing papers is addictive, have to stop
Noweb -> pweave
VCO

% arara: pdflatex: { shell: yes } 
% arara: biber
% arara: pdflatex: { shell: yes }
% arara: clean: { files: [ test.aux, test.log] }

@@

We therefore demonstrate this form factor because, superficially, there are fewer people than there are places.

@@

It has been shown that virions can effect large-scale changes in the electric charges of their [].

>>>>

@@

We therere demonstrate this form factor because, superficially, there are fewer people than there are places.

@@

It has been shown that virions can effect large-scale changes in the electric charges of their \cite{Dynamics2010}.

### 2020-08-06 documents/supplemental.tex
Eppenwolf milled out
VCO

@@

The frequency-dependent inactivation result in Figure 4b is difficult to explain without invoking non-thermal mechanisms. Only one  It is not mentioned how this applied power level was measured.

@@

\cite{EM6969}

@@

Similarly, the gain of the EM-6969 antenna varies from 17 dBi to 21 dBi over the frequency range in Figure 3.

@@

@@

OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarassingly, we were not able to resolve all the dependency issues in order to install it.

We did not discover how little of an effect a wideband sweep would have until late in the project; for this reason, much of the below caters towards wideband circuits and could be greatly simplified for single-frequency operation.

>>>>

\PRLsep{{\itshape Virus structural data }}

One extreme can be seen in

Because CryoEM is sensitive to the

@@

The frequency-dependent inactivation result in Figure 4b of \cite{Efficient2015} is difficult to explain without invoking non-thermal mechanisms. Only one  It is not mentioned how this applied power level was measured.

@@

@@

Similarly, the gain of the EM-6969 antenna\cite{EM6969} varies from 17 dBi to 21 dBi over the frequency range in Figure 3.

@@

Three incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.

\begin{itemize}
	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
	\item The ideal 
	\item The assumption that the only YIG-tuned 
\end{itemize}

There are really two different conflicting criteria:

A low-cost, wide-band

Unfortunately, designing wideband microwave circuits is significantly more difficult than for a particular frequency. Quarter-wavelength

Varactor diodes are a GaAs hyper-abrupt junction diode.

We were warned that this would be difficult:

@@

OpenEMS is excellent, with Python bindings, some lumped components, and mesh refinement. However, embarrassingly, we were not able to resolve all the dependency issues in order to install it.
